How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-23 tse-paper/content.tex
oxford comma

Despite its central role for helping developers and the enablement of
on-ward applications of build logs, the process of how to
automatically analyze build logs has thus far received little
attention as a separate research topic, bringing us to our first
research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What are the state-of-the-research techniques to analyze build logs?
\end{simplebox}

To answer this question, we start our investigation by performing an
extensive literature study (\Cref{fig:overview}).
It shows that
less than half of the 61 works which rely on build log analysis
describe in detail how they performed it, and even fewer
made their implementation available.
The literature
survey identifies three prevalent strategies to
analyze build logs: Using 1) a set of
manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops},
2) information
retrieval techniques,
% TODO: Can you shortly explain the technique here?
and 3) a list of search keywords
to identify regions of interest in the build log.

@@

Finally, we develop a set of guidelines (step 4) on how to choose a
technique given a goal.
We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.
Results
produced by PBE are suited for automatic on-ward processing.
CTS is
well-suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS seems
to be the best choice.
However, its low precision---it extracts a
context of multiple lines around a finding---makes it generally
unsuited for automatic on-ward processing and instead requires a human
to further inspect and interpret the output chunk.
A hybrid-solution combining the three techniques might be the best
allround solution.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the analysis of system
logs which are produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

\subsection{Study Selection}
\Cref{fig:lit-survey} presents an overview of our study selection
process.
Since the field of build log analysis is relatively young, we
surveyed as broad a population of scientific material as possible.
We did not limit our sources to specific Software Engineering
venues~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's
theses and academic slide decks.
We use Google Scholar as opposed to Scopus or
other databases because it is the search engine for academic articles with
the broadest and most current index, including preprints.

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in sufficient detail?'' and
``What is the source of the build logs?'' As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted	data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors
and inspected them as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.
For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.

@@

% TODO It is unclear where this comes from.
% TODO Also, wouldn't it perhaps be better to continue with Figure
4.b directly?
In most cases (51\%), a chunk was retrieved from the log.
Build logs were scanned for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, distinguishing failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

The majority of articles (46\%) used the outcome of their build log
analysis for research purposes, as shown in \Cref{fig:litsur:use}.
% TODO What does this mean? Give an example: to drive further research,
FIXME
for example to categorize the types of compile errors encountered at
Google~\cite{seo2014programmers}.
Further uses were giving feedback to developers (10\%) or automatic
on-ward processing of the retrieved information (8\%)
% TODO for example to ...
FIXME
.

@@

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
% TODO maybe make the point here that it is questionable whether this
%includes a comprehensive tokenizer, lexer etc.
based solution and that parsing in many cases really meant regexp.
If we could figure that out, then we would assign it to regexp instead.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating}
% (based on regular expressions),
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
% based on which technique?,  (based on regular expressions)
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
% based on which technique?  (a parser for the output of make files)
.
% I don't think the based on..
adds something here.

% It's all kinda regex.
Even if we say 'parser' it's often regex in the background

@@

% TODO perhaps remove this paragraph?
% yes it is very unspecific.
however then we have 0 reference
% to how many logs are analyzed
% a central point in our argumentation for automation
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported analyzing from two up to 122 million logs.

@@

% TODO: draw a conclusion together with figure 5: if reuse were higher,
%lots of effort could be saved?
% discussion about popularity of replication packages adds nothing to
this paper.
We observed very little reuse of build log analysis tools.
This can stem from the fact that publishing replication packages and
research prototypes became popular only in recent years or from the
high specialization of the developed tools in regards to supported
build environments and targeted information.

Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
\Cref{fig:litsur:log_producer} shows that many studies and tools target
only a few distinct build environments (roughly, area A).
% TODO: passive ...
The majority of build environments was however only targeted by one
article each (B).
From this, we follow: (a) there is a nichè for custom parsers or even
specialized plugins integrated into the build process to make post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
wrote, still have the disadvantage of not being able to work on historic
builds.
(b) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.
% We implement build environment agnostic build log analysis
% techniques, which are customized to a specific project by
% the training examples which the user provides.
% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
% data set we chose for our evaluation covers a broad range of build
% environments.
% % Further, the training examples also specify the log chunk targeted
% by the
% % retrieval, which enable our chunk retrieval techniques to retrieve
% % a broad range of information from build logs.

@@

We implement three chunk retrieval techniques based on approaches
described by several articles:
PBE mimics regular expressions and parsers while simplifying
their development.
We chose text similarity (CTS) as a common information retrieval
technique, and implement the ad-hoc approach of
searching for specific strings or keywords within KWS\@.

@@

This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
In addition, we present our comparison baseline of random line
retrieval (RLR), illustrate the techniques on a concrete example
of log chunks and sketch out implementation.

@@

% TODO Somehow, we have to find a better place for this.
We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes to late.
The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
In this article, we evaluate different techniques to automatically
retrieve pieces of information that appear literally in the build
logs.
%, i.e., techniques that do not aggregate, combine, or deducted
%information.
We call such pieces of information from build logs
\emph{chunks}, and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

@@

% TODO: these next two sections do not belong under this section --
they are not a chunk retrieval technique.
One way to fix it would be to rename the section.
\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

@@

% TODO This section is not structured well.
First, it misses an
% explanation of the bigger study design.
Second, What is the difference between Study Process and
% Study Design? Third, the LogChunks section appears out of nowhere
% and is not related to the section title (different abstraction
% level).
Perhaps a solution would be to be a bit inspired by this
% paper:
%
https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
% There is a research design section (which we are missing) and a
% Research Method section (which is a mixture of the current section
% titled Log Chunks and Study Process)

@@

To investigate when the chunk retrieval techniques are suited to
analyze build logs (\textbf{RQ2}), we perform an empirical comparison
study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
In particular, we are interested in how many examples a technique
should be trained with (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}) and how reliable the quality of the
produced outputs is (\textbf{RQ2.3}).
This leads us to the following research questions:

@@

In the following, we present the data set we created for this study,
our study process (presented in \Cref{fig:study}) and the metrics
we measure to answer our research questions.

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
they chosen?
% Isn't it rather the case that for each repository, we built traning
sets of size 1, 2,
% ...
5 build logs?
One to five examples make up the training set (2).
% TODO passive ...
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of our techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
of results?
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and our oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% This is a weird position for this paragraph
% TODO What is ``this'' referring to? You just defined a bunch of
equations.
This concludes one execution within our evaluation.
% TODO run vs.
execution above.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the implemented chunk
retrieval
technique.

@@

\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count
				in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example
(PBE)}
\end{figure*}

@@

% TODO introudce this fig at large.
Soemthing like: Zooming in
% on only the successful retrievals from (...), Fig ...
shows ...

@@

\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
precision and recall of the 227 runs where PBE could synthesize a
program consistent with all training examples.
When the training set
size increases from one to two, recall and F$_{1}$-score increase by
about 25\%, precision increases by about 10\%.
For two or more
training examples, recall and F$_{1}$-score stay around 75\% and
precision around 96\%.

@@

\end{subfigure}\hspace{\fill}
\begin{subfigure}[tb]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\end{figure*}

% TODO what about referencing the combined figure at first: something
like shows the results of CTS on two beanplots of ...
and ...., and then the subfigure
% TODO this goes for all techniques
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

\Cref{fig:recall-precision-categorycount-CTS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
With increasing category count, precision,
recall and F$_{1}$-score decrease.
% Especially for more than four
% categories present we have no chunk retrieval runs where all desired
% lines were extracted.

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\end{figure*}

\Cref{fig:recall-precision-examplecount-KWS} presents precision,
recall and F$_{1}$-score of chunk retrieval using KWS for different
numbers of training examples.
The recall increases by about 12\% when
increasing the size of the training set to more than one example,
while the precision stays constant at around 16\%.
The F$_{1}$-score
stays around 26\%.

@@

The baseline of randomly
picking lines from build logs delivers the expected low and
``random'' results: precision ranges between 8\% and 5\% and
recall between 6\% and 8\%.
As expected, the size of the training set has no impact on precision
or recall of retrieving chunks with RLR.
With a larger number of structural categories within the training and
test sets, the precision of RLR decreases from 7\% to 0\%.
Its recall
increases from 6\%, for one structural category present, to 11\%, for
three structural categories present and drops to 0\% again for more
structural categories.

\subsection{Comparison of All Techniques}
In this section, we aggregate and compare the results from
\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.

@@

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
show the influence of all training and test examples being from the
same structural category compared to being multiple categories
For more
than one category being present, the recall of PBE decreases greatly.
% TODO this is not a meaningful comparsion to RLR.
One would be to say that
% all of these techniques beat RLR handsdown
For CTS and KWS the values also decrease, while RLR is not affected by
the number of structural categories present.

@@

% TODO decision tree -> recommendation schema? You can use the more
specific decision
% tree when referencing the figure.
For the interpretation of our study results, we look at each chunk
retrieval technique separately.
We give recommendations for
which types of log chunks and how many training examples
each technique is suited, and
how their output can be used further.
Following that, we discuss
which of these criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on our empirical comparison, we present a
decision tree between the three techniques we investigated.

>>>>

Despite its central role for helping developers and for enabling
applications for on-ward processing of build logs,
the process of how to
automatically analyze build logs has thus far received little
attention as a separate research topic, bringing us to our first
research question:
\begin{simplebox}[minipage boxed title*=-5cm]{\textbf{Research Question
1}}
What are the state-of-the-research techniques to analyze build logs?
\end{simplebox}

To answer this question, we start our investigation by performing an
extensive literature study (\Cref{fig:overview}).
It shows that
less than half of the 61 works which rely on build log analysis
describe in detail how they performed it.
Even fewer
made their implementation available.
The literature
survey identifies three prevalent strategies to
analyze build logs: Using 1) a set of
manually curated regular expressions,
similar to TravisTorrent~\cite{beller2017oops},
2) information
retrieval techniques,
% TODO: Can you shortly explain the technique here?
and 3) a list of search keywords
to identify regions of interest in the build log.

@@

Finally, we develop a set of guidelines (step 4) on how to choose a
technique given a goal.
We recommend PBE for use cases where the desired information is always
represented in the same structural way and high confidence in
precision and recall of the chunk retrieval is required.
Results
produced by PBE are suited for automatic on-ward processing.
CTS is
well-suited when the representation of the desired information varies
slightly and the output of the chunk retrieval is further processed by
a human.
In cases where the textual representation of the desired
information in the log is unpredictable or varies greatly, KWS seems
to be the best choice.
However, its low precision---it extracts a
context of multiple lines around a finding---makes it generally
unsuited for automatic on-ward processing.
Instead, KWS requires a human
to further inspect and interpret the output chunk.
A hybrid-solution combining the three techniques might be the best
all-round solution.

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the analysis of system
logs which are produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level, and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

\subsection{Study Selection}
\Cref{fig:lit-survey} presents an overview of our study selection
process.
Since the field of build log analysis is relatively young, we
surveyed as broad a population of scientific material as possible.
We did not limit our sources to specific Software Engineering
venues~\cite{petersen2015guidelines}, but survey all sources
monitored by Google Scholar, including Bachelor's theses, Master's
theses, and academic slide decks.
We use Google Scholar as opposed to Scopus or
other databases because it is the search engine for academic articles with
the broadest and most current index, including preprints.

@@

To guide the data extraction we created a template.
The template form contained questions to answer RQ 1.1 through RQ 1.3,
for example ``Is the technique explained in detail?'' and
``What is the source of the build logs?''.
As recommended by Petersen et
al.~\cite{petersen2015guidelines}, we started the mapping study with a
pilot study:
both authors extracted data from the same five articles and held a
consensus meeting to unify their understanding
of the data extraction template.
We divided the remaining 46 articles evenly between the two authors
and inspected them as closely as necessary to fill out the template
with confidence,
starting from occurrences of ``log'' or ``build'' within the article's
text.
For questions that did not require a boolean answer, we allowed assigning
multiple tags or categories as the first part (``preparation phase'')
of a virtual open card sorting~\cite{zimmermann2016card}.

@@

% TODO It is unclear where this comes from.
% TODO Also, wouldn't it perhaps be better to continue with Figure
%4.b directly?
In most cases (51\%), a chunk was retrieved from the log.
Build logs were scanned for compilation
errors~\cite{clemencic2014new} or
the duration of tasks within the build~\cite{zhang2016android}.
36\% of the articles classified the build logs into categories.
For instance, distinguishing failures caused by developers from
failures caused
by infrastructure errors~\cite{lindqvist2019detection} or
whether projects use automated static analysis
tools~\cite{kavaler2019tool}.
Other types of information (e.g.,\ counting
lines, summarization) were only retrieved
in one case each.

The majority of articles (46\%) used the outcome of their build log
analysis for research purposes, as shown in \Cref{fig:litsur:use}.
% TODO What does this mean? Give an example: to drive further research,
%FIXME
for example to categorize the types of compile errors encountered at
Google~\cite{seo2014programmers}.
Further uses were giving feedback to developers (10\%) or automatic
on-ward processing of the retrieved information (8\%)
% TODO for example to ...
%FIXME
.

@@

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
% TODO maybe make the point here that it is questionable whether this
%includes a comprehensive tokenizer, lexer etc.
%based solution and that parsing in many cases really meant regexp.
If we could figure that out, then we would assign it to regexp instead.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating}
% (based on regular expressions),
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
% based on which technique?,  (based on regular expressions)
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
% based on which technique?  (a parser for the output of make files)
.
% I don't think the based on..
%adds something here.
% It's all kinda regex.
%Even if we say 'parser' it's often regex in the background

@@

% TODO perhaps remove this paragraph?
% yes it is very unspecific.
%however then we have 0 reference
% to how many logs are analyzed
% a central point in our argumentation for automation
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported analyzing from two up to 122 million logs.

@@

% TODO: draw a conclusion together with figure 5: if reuse were higher,
%lots of effort could be saved?
We observed very little reuse of build log analysis tools.
This can stem from the
high specialization of the developed tools in regards to supported
build environments and targeted information.

Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
\Cref{fig:litsur:log_producer} shows that many studies and tools target
only a few distinct build environments (roughly, area A).
% TODO: passive ...
The majority of build environments was however only targeted by one
article each (B).
From this, we follow: (a) there is a nichè for custom parsers or even
specialized plugins integrated into the build process to make
post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
%TODO cite
wrote, still have the disadvantage of not being able to work on historic
builds.
(b) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.
% We implement build environment agnostic build log analysis
% techniques, which are customized to a specific project by
% the training examples which the user provides.
% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
% data set we chose for our evaluation covers a broad range of build
% environments.
% % Further, the training examples also specify the log chunk targeted
% by the
% % retrieval, which enable our chunk retrieval techniques to retrieve
% % a broad range of information from build logs.

@@

We implement three chunk retrieval techniques based on approaches
described by several articles:
PBE mimics regular expressions and parsers while simplifying
their development.
We chose text similarity (CTS) as a common information retrieval
technique and implement the ad-hoc approach of
searching for specific strings or keywords within KWS\@.

@@

This section introduces key concepts of the three chunk retrieval
techniques we study in this article, namely program synthesis by
example (PBE), common text similarity (CTS), and keyword search (KWS).
In addition, we present our comparison baseline of random line
retrieval (RLR), illustrate the techniques on a concrete example
of log chunks and sketch out their implementation.

@@

% TODO Somehow, we have to find a better place for this.
%We have been
% using the term 'chunk retrieval' beforehand already -- this
% definition now comes to late.
%The first paragraph should already
% apply to the literature mapping, the second of course only applies
% here.

\subsection{Characteristics of Chunk Retrieval Techniques}
\label{sec:crt-characteristics}
In this article, we evaluate different techniques to automatically
retrieve pieces of information that appear literally in the build
logs.
%, i.e., techniques that do not aggregate, combine, or deducted
%information.
We call such pieces of information from build logs
\emph{chunks} and the techniques \emph{chunk retrieval techniques}.
The techniques we investigate here do not require a formal lexer and
parser to analyze the entire structure of build logs, but focus on
ad-hoc extracting just one specific piece of information per
configuration.

@@

% TODO: these next two sections do not belong under this section --
%they are not a chunk retrieval technique.
%One way to fix it would be to rename the section.
\subsection{Chunk Retrieval Example}
\label{sec:crt-example}

@@

% TODO This section is not structured well.
%First, it misses an
% explanation of the bigger study design.
%Second, What is the difference between Study Process and
% Study Design? Third, the LogChunks section appears out of nowhere
% and is not related to the section title (different abstraction
% level).
%Perhaps a solution would be to be a bit inspired by this
% paper:
%https://inventitech.com/publications/2018_beller_spruit_spinellis_zaidman_on_the_dichotomy_of_debugging_behavior_among_programmers.pdf
% There is a research design section (which we are missing) and a
% Research Method section (which is a mixture of the current section
% titled Log Chunks and Study Process)

@@

To investigate when the chunk retrieval techniques are suited to
analyze build logs (\textbf{RQ2}), we perform an empirical comparison
study on the \emph{LogChunks} data set~\cite{brandt2020logchunks}.
In particular, we are interested in how many examples a technique
should be trained with (\textbf{RQ2.1}),
how similar the structural representation of the targeted log chunks
has to be (\textbf{RQ2.2}), and how reliable the quality of the
produced outputs is (\textbf{RQ2.3}).
This leads us to the following research questions:

@@

In the following, we present the data set we created for this study,
our study process (presented in \Cref{fig:study}), and the metrics
we measure to answer our research questions.

@@

\subsection{Study Process}
% TODO: I think you need to introduce a concept that makes clear what one
% ``folder'' consists of ...
% TODO: What does this mean -- we begin by? Aren't we perhaps missing that
% we operate on all repos in LogChunks?
We begin by selecting all examples in \emph{LogChunks}
that correspond to one GitHub repository---and thus the
% TODO () is meant to reference the figure, but this the figure is not
%actually mentioned.
same build environment (1).
% TODO: What does this mean? Of what nature are the examples? How were
%they chosen?
% Isn't it rather the case that for each repository, we built traning
%ets of size 1, 2,
% ...
%5 build logs?
One to five examples make up the training set (2).
% TODO passive ...
We vary its size to measure how many examples are needed to
confidently configure a technique.
The training set is so small because the examples have to be
manually created by a user.
A larger training set would oppose our goal of providing techniques
that can be configured with little effort
(see \Cref{sec:lit-sur:discussion}).
% TODO: The example? why only one? And what is an example? An example
%build log?
% Then it would be good to say so.
The example chronologically after the training set makes up the
test set (3).
In this way, we train on examples from past build logs and test on
more recent logs.
We chose a test set size of 1, as users of our techniques
should receive reliable results on every build log they analyze.
% TODO and why is this important? Doesn't everyone want such stability
of results?
In the next step, we configure a chunk retrieval technique with
the examples from the training set (4) and apply the technique to the
training set (5), which produces the retrieval output (6).
Based on this, we collect the following measurements (7):
the size of the training set (\textbf{RQ2.1}),
the number of structural categories in the training
set (\textbf{RQ2.2}),
the lines of the retrieval output ($\mathit{RetrievedLines}$),
and our oracle: the output defined in the test example
($\mathit{DesiredLines}$).
From these we calculate accuracy metrics (\textbf{RQ2.3}):

@@

% This is a weird position for this paragraph
% TODO What is ``this'' referring to? You just defined a bunch of
%equations.
This concludes one execution within our evaluation.
% TODO run vs.
%execution above.
We conduct one run for each of the four chunk retrieval techniques,
for each of the eighty repositories in \emph{LogChunks} (8)
and for each of the five training set sizes (2).
In total we perform 1600 runs, 400 for each of the implemented chunk
retrieval
technique.

@@

\begin{figure*}
\centering
    \textbf{Program Synthesis by Example (PBE)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
				\caption{Successfulness of retrieval
				compared by structural category count
				in training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
				\caption{Precision, recall, and
				F$_{1}$-score when PBE could synthesize
				a consistent program compared with the
				size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example
(PBE)}
\end{figure*}

@@

% TODO introudce this fig at large.
%Soemthing like: Zooming in
% on only the successful retrievals from (...), Fig ...
%shows ...

@@

\Cref{fig:recall-precision-examplecount-sythesisworked-PBE} shows
precision and recall of the 227 runs where PBE could synthesize a
program consistent with all training examples.
When the training set
size increases from one to two, recall, and F$_{1}$-score increase by
about 25\%, precision increases by about 10\%.
For two or more
training examples, recall, and F$_{1}$-score stay around 75\% and
precision around 96\%.

@@

\end{subfigure}\hspace{\fill}
\begin{subfigure}[tb]{\columnwidth}
		\centering
				\includegraphics[width=\columnwidth,
				clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{structural category count
		in training and test set.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Precision, recall, and F$_{1}$-score of chunk
retrieval with Common Text Similarity (CTS) compared by \ldots}
\end{figure*}

% TODO what about referencing the combined figure at first: something
%like shows the results of CTS on two beanplots of ...
%and ...., and then the subfigure
% TODO this goes for all techniques
\Cref{fig:recall-precision-examplecount-CTS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using CTS for an
increasing number of training examples.
When using one to five
training examples, the size of the training set has no noticeable
influence on precision, recall or F$_{1}$-score of the chunk retrieval
with CTS.

\Cref{fig:recall-precision-categorycount-CTS} shows the same
measurements for an increasing number of structural categories in the
training and test examples.
With increasing category count, precision,
recall, and F$_{1}$-score decrease.
% Especially for more than four
% categories present we have no chunk retrieval runs where all desired
% lines were extracted.

\subsection{Keyword Search (KWS)}
\label{sec:r:kws}
\begin{figure*}
\centering
    \textbf{Keyword Search (KWS)}\par\medskip
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{structural category count
		in training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Precision, recall, and F$_{1}$-score of chunk retrieval with
Keyword Search (KWS) compared by \ldots}
\end{figure*}

\Cref{fig:recall-precision-examplecount-KWS} presents precision,
recall, and F$_{1}$-score of chunk retrieval using KWS for different
numbers of training examples.
The recall increases by about 12\% when
increasing the size of the training set to more than one example,
while the precision stays constant at around 16\%.
The F$_{1}$-score
stays around 26\%.

@@

The baseline of randomly
picking lines from build logs delivers the expected low and
``random'' results: precision ranges between 8\% and 5\%,
recall between 6\% and 8\%.
As expected, the size of the training set has no impact on precision
or recall of retrieving chunks with RLR.
With a larger number of structural categories within the training and
test sets, the precision of RLR decreases from 7\% to 0\%.
Its recall
increases from 6\%, for one structural category present, to 11\%, for
three structural categories present and drops to 0\% again for more
structural categories.

\subsection{Comparison of All Techniques}
%TODO too short
In this section, we aggregate and compare the results from
\Cref{sec:r:kws,sec:r:pbe,sec:r:cts,sec:r:rlr}.

@@

\Cref{fig:recall-precision-singlecategory-all,fig:recall-precision-multicategory-all}
show the influence of all training and test examples being from the
same structural category compared to being multiple categories
For more
than one category being present, the recall of PBE decreases greatly.
% TODO this is not a meaningful comparsion to RLR.
%One would be to say that
% all of these techniques beat RLR handsdown
For CTS and KWS the values also decrease, while RLR is not affected by
the number of structural categories present.

@@

% TODO decision tree -> recommendation schema? You can use the more
%specific decision
% tree when referencing the figure.
For the interpretation of our study results, we look at each chunk
retrieval technique separately.
We give recommendations for
which types of log chunks and how many training examples
each technique is suited, as well as
how their output can be used further.
Following that, we discuss
which of these criteria should influence the decision to use a certain
chunk retrieval technique most.
Based on our empirical comparison, we present a
decision tree between the three techniques we investigated.
